The problem and promise of scale in multilayer networks

### 2020-02-04 paper/manuscript.Rmd
reorg so figs are before results

# Scale in multilayer networks in practice: case study results and discussion

>>>>

# Scale in multilayer networks in practice: case study results and discussion
<!-- FIGURES ----------------------- -->

```{r socres, fig.cap='(ref:socres)'}
knitr::include_graphics('../graphics/figure-spatialthreshold.png')
```

```{r lcres, fig.cap='(ref:lcres)'}
knitr::include_graphics('../graphics/figure-lcres.png')
```

```{r nobs, fig.cap='(ref:nobs)'}
knitr::include_graphics('../graphics/figure-nobs.png')
```

```{r winlen, fig.cap='(ref:winlen)'}
knitr::include_graphics('../graphics/figure-winlength.png')
```

```{r winpos, fig.cap='(ref:winpos)'}
knitr::include_graphics('../graphics/figure-winpos.png')
```

<!-- RESULTS / DISCUSSION --------------------------- -->
